TODO

### 2025-01-03 write-ups/kid_tangrams_cogsci_2025/kid_tangrams_cogsci_2025.Rmd
added age ranges

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, 
                      fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, 
                      message=F, sanitize = T)

@@

# experiment 1 imports
transcript_1 <- read_csv(here(expt_1,"timed_transcript.csv"))
dat_1 <- read_csv(here(expt_1, "clean_data.csv")) |> rename(trial=trialNum)
exclusion_1 <- transcript_1 %>% filter(!is.na(description)) %>% filter(role=="S") %>% select(game, trial) %>% unique() %>% mutate("S_talked"=1)

words_1 <- transcript_1 |> filter(!is.na(description)) |> mutate(words=description |> str_count("\\S+")) |> 
  filter(role=="S") |> 
  group_by(game, trial) |> 
  summarize(words=sum(words))

clean_1 <- dat_1 %>% left_join(exclusion_1) %>% filter(S_talked==1) |> left_join(words_1) |>  mutate(type=case_when(trial<2 ~ "practice",
                        trial<6 ~ "block 1",
                        trial<10 ~ "block 2",
                        trial<14 ~ "block 3"))

sims_1 <- read_rds(here(expt_1,"similarities.rds")) |>
    as_tibble() |> 
  inner_join(clean_1|> select(game1 = game, trial1 = trial, target1 = target, speaker1 = speaker)) |>
  inner_join(clean_1 |> select(game2 = game, trial2 = trial, target2 = target, speaker2 = speaker)) |>
  filter(target1 == target2) |>
  filter(trial1>1) |> 
  filter(trial2>1) |> 
  mutate(trial1=trial1+2,
         trial2=trial2+2) |> 
  mutate(block1 = trial1 %/% 4, block2 = trial2 %/% 4) |>
  mutate(same_speaker=(speaker1==speaker2) |> as.numeric(),
         same_game=(game1==game2) |> as.numeric(),
        later = ifelse(block1 > block2, block1, block2),
        earlier = ifelse(block1 > block2, block2, block1)) |> mutate(target=target1)

@@

words_2 <- transcript_2 |> mutate(words=description |> str_count("\\S+")) |> 
  filter(role=="S") |> 
  group_by(gameId, gameConfig, trial) |> 
  summarize(words=sum(words))

clean_2 <- data_2 |> left_join(words_2) |>
  filter(!is.na(words)) |> 
   mutate(type = case_when(
    trial < 4 ~ "practice",
    trial < 8 ~ "block 1",
    trial < 12 ~ "block 2",
    trial < 16 ~ "block 3",
    trial < 20 ~ "block 4"
  )) |>
  filter(!is.na(response)) |> 
  mutate(correct=as.numeric(correct))

sims_2 <- read_rds(here(expt_2, "similarities.rds")) |>
  as_tibble() |>
  inner_join(clean_2 |> select(game1 = gameId, trial1 = trial, target1 = target, speaker1 = speaker)) |>
  inner_join(clean_2 |> select(game2 = gameId, trial2 = trial, target2 = target, speaker2 = speaker)) |>
  filter(target1 == target2) |>
  mutate(block1 = trial1 %/% 4, block2 = trial2 %/% 4) |>
  mutate(same_speaker=(speaker1==speaker2) |> as.numeric(),
         same_game=(game1==game2) |> as.numeric(),
        later = ifelse(block1 > block2, block1, block2),
        earlier = ifelse(block1 > block2, block2, block1)) |> mutate(target=target1)
```

```{r, eval=F}

library(tidybayes)

@@

mods <- list.files(path = here(mod_loc), pattern = ".*rds") |> walk(~ do_model(.))

```

@@

  str_c(dep, " ~ ", ind) |>
    str_replace_all(" ", "") |>
    str_replace_all("\\*", " $\\\\times$ ") |>
    str_replace_all("\\+", "&nbsp;+ ") |>
    str_replace_all("~", "$\\\\sim$ ")
}

```

@@

## Participants
4 and 5 year old children were recruited from a university nursery school during the school day. Children played with another child from the same class. Experiment 1 was conducted between June and August 2023. Pairs of children were included in analyses if they completed at least 8 of the 12 critical trials. We had 19 complete games and 1 incomplete, but included game. TODO children's age range + median and gender split.

@@

```{r interface, fig.env = "figure*", fig.pos = "t!", fig.width=6, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "TODO \\label{game}", cache=FALSE}

```

@@

```{r fig-accuracy, fig.env="figure", fig.pos = "t", fig.align = "center", out.width="100%", fig.width=5, fig.height=3, fig.cap = "Children's accuracy at selecting the correct target over time. Experiment 1 had 3 blocks (12 total critical trials) and experiment 2 had 4 blocks (16 critical trials). Error bars are bootstrapped 95% CIs with a linear trend line overlaid. \\label{acc}" }
clean_2 |>
    filter(type!="practice") |> mutate(trial=trial-3, expt="Expt 2") |> 
  bind_rows(clean_1 |> filter(type!="practice") |> mutate(trial=trial-1, expt="Expt 1")) |> 
  ggplot(aes(x = trial, y = correct)) +
  stat_summary(aes(fill = type), fun.data = "mean_cl_boot", geom = "bar") +
  stat_summary(fun.data = "mean_cl_boot", geom = "linerange", color = "black") +
  scale_fill_manual(values = time_palette) +
  # geom_bar(position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  geom_smooth(method = "lm", color = "black") +
  # geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  xlab("Trial") +
  ylab("Accuracy") +
  scale_x_continuous(breaks = seq(1, 16, 4), expand = c(0, 0)) +
  scale_y_continuous(breaks = seq(0, 1, .2), expand = c(0, 0)) +
  geom_hline(yintercept = .5) +
  facet_grid(expt~.)+
  theme(legend.position = "none",
        panel.grid = element_blank(),
        strip.background = element_blank())
```

```{r, eval=F}
acc_priors <- c(
set_prior("normal(0,1)", class="b"),
set_prior("normal(0,1)", class="sd"),
set_prior("lkj(1)", class="cor")
)

acc_mod_data_1 <- clean_1 |> mutate(correct.num=ifelse(correct==TRUE, 1,0),
                                  trial.num=trial-2) |> filter(type!="practice")
acc_mod_1 <- brm(correct.num ~ trial.num + (trial.num|game) + (1|target),
               family = bernoulli(link = "logit"),
               data=acc_mod_data_1,
               file = here(mod_loc, "acc_1.rds"),
               prior=acc_priors,
               control = list(adapt_delta=.95))
```

```{r}
acc_mod_1 <- read_rds(here(mod_results, "acc_1.rds")) |> mutate(across(c(`Estimate`,`lower`,`upper`), ~exp(.)))

acc_form <- read_rds(here(mod_form,"acc_1.rds"))
```

@@

```{r, eval=F}

speed_priors <- c(
  set_prior("normal(60,100)", class="Intercept"),
set_prior("normal(0,20)", class="b"),
set_prior("normal(0,20)", class="sd"),
set_prior("lkj(1)", class="cor")
)

speed_mod_data_1 <- clean_1 |> mutate(time.sec=time/1000,
                                  trial.num=trial-2) |> filter(type!="practice")

speed_mod_1 <- brm(time.sec ~ trial.num + (trial.num|game) + (1|target),
               data=speed_mod_data_1,
               file = here(mod_loc, "speed_1.rds"),
               prior=speed_priors,
               control = list(adapt_delta=.95))
```

@@

```{r, eval=F}

description_priors <- c(
  set_prior("normal(5,10)", class="Intercept"),
set_prior("normal(0,5)", class="b"),
set_prior("normal(0,5)", class="sd"),
set_prior("lkj(1)", class="cor")
)

description_mod_data_1 <- clean_1 |> mutate(
                                  trial.num=trial-2) |> filter(type!="practice")

description_mod_1 <- brm(words ~ trial.num + (trial.num|game) + (1|target),
               data=description_mod_data_1,
               file = here(mod_loc, "description_1.rds"),
               prior=speed_priors,
               control = list(adapt_delta=.95))

```

```{r description, fig.env="figure", fig.pos = "t", fig.align = "center", out.width="100%", fig.width=5, fig.height=3, fig.cap = "Length of referential expression (in words) produced by the speaker each trial. Grey dots are individual data points, colored dots are per trial means with bootstrapped 95% CIs. \\label{length}" }

clean_2 |>
    filter(type!="practice") |> mutate(trial=trial-3, expt="Expt 2") |> 
  bind_rows(clean_1 |> filter(type!="practice") |> mutate(trial=trial-1, expt="Expt 1")) |> ggplot( aes(x = trial, y = words, color = type)) +
  geom_jitter(alpha = .5, color = "grey") +
  stat_summary(fun.data = "mean_cl_boot") +
  scale_x_continuous(breaks = seq(1, 20, 1), expand = c(0, 0)) +
  scale_color_manual(values = time_palette) +
  geom_smooth(method = "lm", color = "black") +
  xlab("Trial") +
  ylab("Words") +
  facet_grid(expt~.)+
  theme(legend.position = "none",
        panel.grid = element_blank(),
        strip.background = element_blank())
```

@@

description_form <- read_rds(here(mod_form, "description_1.rds"))

```

@@

```{r sims, fig.env="figure", fig.pos = "t", fig.align = "center", out.width="100%", fig.width=5, fig.height=3, fig.cap = "Semantic similarity between referential descriptions from the speaker to the same target under different circumstances. Different games refers to similarities across two speakers from different games, same game to similarities across the two participants in one game, and same speaker to descriptions from the same person in different blocks. Dots are means and lines are bootstrapped 95% CIs.  \\label{sim}" }

sims_2 |>
  mutate(source = case_when(
    speaker1 == speaker2 ~ "same speaker",
    game1 == game2 ~ "same game",
    T ~ "different games"
  )) |> mutate(expt="Expt 2") |> 
  bind_rows(sims_1 |>
  mutate(source = case_when(
    speaker1 == speaker2 ~ "same speaker",
    game1 == game2 ~ "same game",
    T ~ "different games"
  )) |> mutate(expt="Expt 1")) |> 
  ggplot(aes(x = source, y = sim, color = target1)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  labs(y = "Cosine similarity", x = "Comparing two utterances from ...", color = "target image") +
  facet_grid(expt~.)+
  scale_color_solarized()+
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        strip.background = element_blank())

```

@@

```{r include=F}
sims_1 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == earlier + 1) |>
  mutate(same_speaker = ifelse(speaker1 == speaker2, "same speaker", "different speaker")) |>
  ggplot(aes(as.character(earlier), sim, color = target1)) +
  geom_point(alpha = .1, position = position_dodge(width = .2)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  facet_wrap(~same_speaker) +
  labs(x = "Earlier block to *next* block", y = "cosine similarity", color = "target") +
  theme(legend.position = "bottom")

```

@@

Following cite Boyce et al 2024, we use Sentence-BERT to embed the descriptions in a semantic vector space, and then use the cosine between embeddings as a measure of semantic similarity between descriptions. We compare the semantic similarities between descriptions of the same target based on who produced the description. Our question is whether the two children within the same game produce descriptions that are more similar to each other than two children in different games. As shown in Figure \ref{sim}, different children in the same game do produce more similar descriptions than children in different games, although the descriptions are less similar than descriptions from the same child in different rounds. This provides weak evidence for some coordination between chidren.

@@

TODO should we run the brms model on this?

@@

## Participants
Experiment 2 was run between March and August of 2024, at the same university preschool as experiment 1. No children participated in both experiments. 30 pairs of children completed all 16 critical trials, and 1 pair of children completed between 8 and 16 critical trials. TODO mention that one kid was actually too young TODO mention age range / median and gender distribution.

@@

```{r, eval=F}
acc_priors <- c(
set_prior("normal(0,1)", class="b"),
set_prior("normal(0,1)", class="sd"),
set_prior("lkj(1)", class="cor")
)

acc_mod_data <- clean_2 |> mutate(correct.num=ifelse(correct==TRUE, 1,0),
                                  trial.num=trial-4) |> filter(type!="practice")
acc_mod <- brm(correct.num ~ trial.num + (trial.num|gameId) + (1|target),
               family = bernoulli(link = "logit"),
               data=acc_mod_data,
               file = here(mod_loc, "acc_2.rds"),
               prior=acc_priors,
               control = list(adapt_delta=.95))
```

```{r}
acc_mod_2 <- read_rds(here(mod_results, "acc_2.rds")) |> mutate(across(c(`Estimate`,`lower`,`upper`), ~exp(.)))

```

@@

```{r}

speed_priors <- c(
  set_prior("normal(60,100)", class="Intercept"),
set_prior("normal(0,20)", class="b"),
set_prior("normal(0,20)", class="sd"),
set_prior("lkj(1)", class="cor")
)

speed_mod_data_2<- clean_2 |> mutate(time.sec=time/1000,
                                  trial.num=trial-2) |> filter(type!="practice")

speed_mod_2 <- brm(time.sec ~ trial.num + (trial.num|gameId) + (1|target),
               data=speed_mod_data_2,
               file = here(mod_loc, "speed_2.rds"),
               prior=speed_priors,
               control = list(adapt_delta=.95))
```

```{r}
speed_mod_2 <- read_rds(here(mod_results, "speed_2.rds"))

```

@@

```{r, eval=F}

description_priors <- c(
  set_prior("normal(5,10)", class="Intercept"),
set_prior("normal(0,5)", class="b"),
set_prior("normal(0,5)", class="sd"),
set_prior("lkj(1)", class="cor")
)

description_mod_data_2 <- clean_2 |> mutate(
                                  trial.num=trial-2) |> filter(type!="practice")

description_mod_2 <- brm(words ~ trial.num + (trial.num|gameId) + (1|target),
               data=description_mod_data_2,
               file = here(mod_loc, "description_2.rds"),
               prior=speed_priors,
               control = list(adapt_delta=.95))
```

```{r}
description_mod_2 <- read_rds(here(mod_results, "description_2.rds"))

```

@@

```{r}
conv_priors <- c(
  set_prior("normal(.5,.2)", class="Intercept"),
set_prior("normal(0,.1)", class="b"),
set_prior("normal(0,.05)", class="sd")
)

@@

sim_across_between_mod_2 <- brm(sim ~ same_game + same_speaker+ (1|target),
               data=sim_across_between_data_2,
               file = here(mod_loc, "sim_across_between_2.rds"),
               prior=conv_priors,
               control = list(adapt_delta=.95))

sim_to_last_data_2 <- sims_2 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == 4) |> 
    mutate(same_speaker = ifelse(speaker1 == speaker2, 1, 0),
           earlier_block.num=earlier-1)

sim_to_last_mod_2 <- brm(sim ~ earlier_block.num+ same_speaker+ (1|game1)+(1|target),
               data=sim_to_last_data_2,
               file = here(mod_loc, "sim_to_last_2.rds"),
               prior=conv_priors,
               control = list(adapt_delta=.95))

sim_to_next_data_2 <- sims_2 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == earlier+1) |> 
    mutate(same_speaker = ifelse(speaker1 == speaker2, 1, 0),
           earlier_block.num=earlier-1)

sim_to_next_mod_2 <- brm(sim ~ earlier_block.num+ same_speaker+ (1|game1)+(1|target),
               data=sim_to_next_data_2,
               file = here(mod_loc, "sim_to_next_2.rds"),
               prior=conv_priors,
               control = list(adapt_delta=.95))

sim_across_data_2 <- sims_2 |>
  filter(game1 != game2) |>
  filter(block1 == block2) |> 
    mutate(block.num=block1-1)

sim_across_mod_2 <- brm(sim ~ block.num+(1|target),
               data=sim_across_data_2,
               file = here(mod_loc, "sim_across_2.rds"),
               prior=conv_priors,
               control = list(adapt_delta=.95))

```

>>>>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 3, fig.height = 3, fig.crop = F,
  fig.pos = "tb", fig.path = "figs/",
  echo = F, warning = F, cache = F,
  message = F, sanitize = T
)

@@

# experiment 1 imports
transcript_1 <- read_csv(here(expt_1, "timed_transcript.csv"))
dat_1 <- read_csv(here(expt_1, "clean_data.csv")) |> rename(trial = trialNum)
exclusion_1 <- transcript_1 %>%
  filter(!is.na(description)) %>%
  filter(role == "S") %>%
  select(game, trial) %>%
  unique() %>%
  mutate("S_talked" = 1)

words_1 <- transcript_1 |>
  filter(!is.na(description)) |>
  mutate(words = description |> str_count("\\S+")) |>
  filter(role == "S") |>
  group_by(game, trial) |>
  summarize(words = sum(words))

clean_1 <- dat_1 %>%
  left_join(exclusion_1) %>%
  filter(S_talked == 1) |>
  left_join(words_1) |>
  mutate(type = case_when(
    trial < 2 ~ "practice",
    trial < 6 ~ "block 1",
    trial < 10 ~ "block 2",
    trial < 14 ~ "block 3"
  ))

sims_1 <- read_rds(here(expt_1, "similarities.rds")) |>
  as_tibble() |>
  inner_join(clean_1 |> select(game1 = game, trial1 = trial, target1 = target, speaker1 = speaker)) |>
  inner_join(clean_1 |> select(game2 = game, trial2 = trial, target2 = target, speaker2 = speaker)) |>
  filter(target1 == target2) |>
  filter(trial1 > 1) |>
  filter(trial2 > 1) |>
  mutate(
    trial1 = trial1 + 2,
    trial2 = trial2 + 2
  ) |>
  mutate(block1 = trial1 %/% 4, block2 = trial2 %/% 4) |>
  mutate(
    same_speaker = (speaker1 == speaker2) |> as.numeric(),
    same_game = (game1 == game2) |> as.numeric(),
    later = ifelse(block1 > block2, block1, block2),
    earlier = ifelse(block1 > block2, block2, block1)
  ) |>
  mutate(target = target1)

@@

words_2 <- transcript_2 |>
  mutate(words = description |> str_count("\\S+")) |>
  filter(role == "S") |>
  group_by(gameId, gameConfig, trial) |>
  summarize(words = sum(words))

clean_2 <- data_2 |>
  left_join(words_2) |>
  filter(!is.na(words)) |>
  mutate(type = case_when(
    trial < 4 ~ "practice",
    trial < 8 ~ "block 1",
    trial < 12 ~ "block 2",
    trial < 16 ~ "block 3",
    trial < 20 ~ "block 4"
  )) |>
  filter(!is.na(response)) |>
  mutate(correct = as.numeric(correct))

sims_2 <- read_rds(here(expt_2, "similarities.rds")) |>
  as_tibble() |>
  inner_join(clean_2 |> select(game1 = gameId, trial1 = trial, target1 = target, speaker1 = speaker)) |>
  inner_join(clean_2 |> select(game2 = gameId, trial2 = trial, target2 = target, speaker2 = speaker)) |>
  filter(target1 == target2) |>
  mutate(block1 = trial1 %/% 4, block2 = trial2 %/% 4) |>
  mutate(
    same_speaker = (speaker1 == speaker2) |> as.numeric(),
    same_game = (game1 == game2) |> as.numeric(),
    later = ifelse(block1 > block2, block1, block2),
    earlier = ifelse(block1 > block2, block2, block1)
  ) |>
  mutate(target = target1)
```

```{r, eval=F}
library(tidybayes)

@@

mods <- list.files(path = here(mod_loc), pattern = ".*rds") |> walk(~ do_model(.))
```

@@

  str_c(dep, " ~ ", ind) |>
    str_replace_all(" ", "") |>
    str_replace_all("\\*", " $\\\\times$ ") |>
    str_replace_all("\\+", "&nbsp;+ ") |>
    str_replace_all("~", "$\\\\sim$ ")
}
```

@@

## Participants
4 and 5 year old children were recruited from a university nursery school during the school day. Children played with another child from the same class. Experiment 1 was conducted between June and August 2023. Pairs of children were included in analyses if they completed at least 8 of the 12 critical trials. We had 19 complete games and 1 incomplete, but included game. Of the 40 children, 21 were girls, and the median age was 57 months, with a range of 48-70 months.

```{r, eval=F}
# demo <- read_csv(here("demographics.csv")) |>
#   filter(included == "x") |>
#   mutate(date_test = mdy(date_test), date_birth = mdy(date_birth)) |>
#   select(date_test, date_birth, gender) |>
#   mutate(
#     age = date_test - date_birth,
#     age = as.numeric(age) / 365.25 * 12
#   ) |> 
#   mutate(expt=ifelse(date_test>ymd("2024-01-01"), "expt2", "expt1")) |> 
#   group_by(expt) |> 
#   summarize(female=sum(gender=="female"),
#             total=n(),
#             median=median(age),
#             min=min(age),
#             max=max(age))
```

@@

```{r interface, fig.env = "figure*", fig.pos = "t!", fig.width=6, fig.height=2, fig.align = "center", set.cap.width=T, num.cols.cap=2, fig.cap = "TODO \\label{game}", cache=FALSE}
```

@@

```{r fig-accuracy, fig.env="figure", fig.pos = "t", fig.align = "center", out.width="100%", fig.width=5, fig.height=3, fig.cap = "Children's accuracy at selecting the correct target over time. Experiment 1 had 3 blocks (12 total critical trials) and experiment 2 had 4 blocks (16 critical trials). Error bars are bootstrapped 95% CIs with a linear trend line overlaid. \\label{acc}" }
clean_2 |>
  filter(type != "practice") |>
  mutate(trial = trial - 3, expt = "Expt 2") |>
  bind_rows(clean_1 |> filter(type != "practice") |> mutate(trial = trial - 1, expt = "Expt 1")) |>
  ggplot(aes(x = trial, y = correct)) +
  stat_summary(aes(fill = type), fun.data = "mean_cl_boot", geom = "bar") +
  stat_summary(fun.data = "mean_cl_boot", geom = "linerange", color = "black") +
  scale_fill_manual(values = time_palette) +
  # geom_bar(position = position_dodge(.9), color = "black", fill = "#19ADDE", width = .7) +
  geom_smooth(method = "lm", color = "black") +
  # geom_text(aes(label = percent), hjust = 1.6, color = "white", size = 3) +
  xlab("Trial") +
  ylab("Accuracy") +
  scale_x_continuous(breaks = seq(1, 16, 4), expand = c(0, 0)) +
  scale_y_continuous(breaks = seq(0, 1, .2), expand = c(0, 0)) +
  geom_hline(yintercept = .5) +
  facet_grid(expt ~ .) +
  theme(
    legend.position = "none",
    panel.grid = element_blank(),
    strip.background = element_blank()
  )
```

```{r, eval=F}
acc_priors <- c(
  set_prior("normal(0,1)", class = "b"),
  set_prior("normal(0,1)", class = "sd"),
  set_prior("lkj(1)", class = "cor")
)

acc_mod_data_1 <- clean_1 |>
  mutate(
    correct.num = ifelse(correct == TRUE, 1, 0),
    trial.num = trial - 2
  ) |>
  filter(type != "practice")
acc_mod_1 <- brm(correct.num ~ trial.num + (trial.num | game) + (1 | target),
  family = bernoulli(link = "logit"),
  data = acc_mod_data_1,
  file = here(mod_loc, "acc_1.rds"),
  prior = acc_priors,
  control = list(adapt_delta = .95)
)
```

```{r}
acc_mod_1 <- read_rds(here(mod_results, "acc_1.rds")) |> mutate(across(c(`Estimate`, `lower`, `upper`), ~ exp(.)))

acc_form <- read_rds(here(mod_form, "acc_1.rds"))
```

@@

```{r, eval=F}
speed_priors <- c(
  set_prior("normal(60,100)", class = "Intercept"),
  set_prior("normal(0,20)", class = "b"),
  set_prior("normal(0,20)", class = "sd"),
  set_prior("lkj(1)", class = "cor")
)

speed_mod_data_1 <- clean_1 |>
  mutate(
    time.sec = time / 1000,
    trial.num = trial - 2
  ) |>
  filter(type != "practice")

speed_mod_1 <- brm(time.sec ~ trial.num + (trial.num | game) + (1 | target),
  data = speed_mod_data_1,
  file = here(mod_loc, "speed_1.rds"),
  prior = speed_priors,
  control = list(adapt_delta = .95)
)
```

@@

```{r, eval=F}
description_priors <- c(
  set_prior("normal(5,10)", class = "Intercept"),
  set_prior("normal(0,5)", class = "b"),
  set_prior("normal(0,5)", class = "sd"),
  set_prior("lkj(1)", class = "cor")
)

description_mod_data_1 <- clean_1 |>
  mutate(
    trial.num = trial - 2
  ) |>
  filter(type != "practice")

description_mod_1 <- brm(words ~ trial.num + (trial.num | game) + (1 | target),
  data = description_mod_data_1,
  file = here(mod_loc, "description_1.rds"),
  prior = speed_priors,
  control = list(adapt_delta = .95)
)
```

```{r description, fig.env="figure", fig.pos = "t", fig.align = "center", out.width="100%", fig.width=5, fig.height=3, fig.cap = "Length of referential expression (in words) produced by the speaker each trial. Grey dots are individual data points, colored dots are per trial means with bootstrapped 95% CIs. \\label{length}" }
clean_2 |>
  filter(type != "practice") |>
  mutate(trial = trial - 3, expt = "Expt 2") |>
  bind_rows(clean_1 |> filter(type != "practice") |> mutate(trial = trial - 1, expt = "Expt 1")) |>
  ggplot(aes(x = trial, y = words, color = type)) +
  geom_jitter(alpha = .5, color = "grey") +
  stat_summary(fun.data = "mean_cl_boot") +
  scale_x_continuous(breaks = seq(1, 20, 1), expand = c(0, 0)) +
  scale_color_manual(values = time_palette) +
  geom_smooth(method = "lm", color = "black") +
  xlab("Trial") +
  ylab("Words") +
  facet_grid(expt ~ .) +
  theme(
    legend.position = "none",
    panel.grid = element_blank(),
    strip.background = element_blank()
  )
```

@@

description_form <- read_rds(here(mod_form, "description_1.rds"))
```

@@

```{r}
conv_priors <- c(
  set_prior("normal(.5,.2)", class = "Intercept"),
  set_prior("normal(0,.1)", class = "b"),
  set_prior("normal(0,.05)", class = "sd")
)

sim_across_between_data_1 <- sims_1 |>
  mutate(same_game = case_when(
    game1 == game2 ~ 1,
    T ~ 0
  )) |>
  mutate(same_speaker = ifelse(speaker1 == speaker2, 1, 0))

sim_across_between_mod_1 <- brm(sim ~ same_game + same_speaker + (1 | target),
  data = sim_across_between_data_1,
  file = here(mod_loc, "sim_across_between_1.rds"),
  prior = conv_priors,
  control = list(adapt_delta = .95)
)
```

```{r sims, fig.env="figure", fig.pos = "t", fig.align = "center", out.width="100%", fig.width=5, fig.height=3, fig.cap = "Semantic similarity between referential descriptions from the speaker to the same target under different circumstances. Different games refers to similarities across two speakers from different games, same game to similarities across the two participants in one game, and same speaker to descriptions from the same person in different blocks. Dots are means and lines are bootstrapped 95% CIs.  \\label{sim}" }
sims_2 |>
  mutate(source = case_when(
    speaker1 == speaker2 ~ "same speaker",
    game1 == game2 ~ "same game",
    T ~ "different games"
  )) |>
  mutate(expt = "Expt 2") |>
  bind_rows(sims_1 |>
    mutate(source = case_when(
      speaker1 == speaker2 ~ "same speaker",
      game1 == game2 ~ "same game",
      T ~ "different games"
    )) |> mutate(expt = "Expt 1")) |>
  ggplot(aes(x = source, y = sim, color = target1)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  labs(y = "Cosine similarity", x = "Comparing two utterances from ...", color = "target image") +
  facet_grid(expt ~ .) +
  scale_color_solarized() +
  theme(
    legend.position = "bottom",
    panel.grid = element_blank(),
    strip.background = element_blank()
  )
```

```{r}
sim_across_between_1_results <- read_rds(here(mod_results, "sim_across_between_1.rds"))

sim_across_between_form <- read_rds(here(mod_form, "sim_across_between_1.rds"))
```

@@

```{r include=F}
sims_1 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == earlier + 1) |>
  mutate(same_speaker = ifelse(speaker1 == speaker2, "same speaker", "different speaker")) |>
  ggplot(aes(as.character(earlier), sim, color = target1)) +
  geom_point(alpha = .1, position = position_dodge(width = .2)) +
  stat_summary(fun.data = "mean_cl_boot", position = position_dodge(width = .2)) +
  facet_wrap(~same_speaker) +
  labs(x = "Earlier block to *next* block", y = "cosine similarity", color = "target") +
  theme(legend.position = "bottom")
```

@@

Following cite Boyce et al 2024, we use Sentence-BERT to embed the descriptions in a semantic vector space, and then use the cosine between embeddings as a measure of semantic similarity between descriptions. We compare the semantic similarities between descriptions of the same target based on who produced the description. Our question is whether the two children within the same game produce descriptions that are more similar to each other than two children in different games. As shown in Figure \ref{sim}, different children in the same game do produce more similar descriptions than children in different games, although the descriptions are less similar than descriptions from the same child in different rounds. We modeled this as `r sim_across_between_form |> form()`. Utterances were more similar if they came from the same partnership (`r sim_across_between_1_results |> stats_text(2,3)`) and were slightly more similar still if they came from the same person with the partnership (`r sim_across_between_1_results |> stats_text(3,3)`). The big differences in descriptions between games compared to within games is a measure of partner sensitivity -- children are more likely to use descriptions semantically similar to their partner's than to another child's. This provides weak evidence for some coordination between chidren.

@@

@@

## Participants
Experiment 2 was run between March and August of 2024, at the same university preschool as experiment 1. No children participated in both experiments. 30 pairs of children completed all 16 critical trials, and 1 pair of children completed between 8 and 16 critical trials. Our target age range was 4 and 5 year olds, but one almost 4-year-old was unintentionally included. Of the 62 children, 30 were girls, and the children had a median age of 56 months, and a range of 45-69 months.

@@

```{r, eval=F}
acc_priors <- c(
  set_prior("normal(0,1)", class = "b"),
  set_prior("normal(0,1)", class = "sd"),
  set_prior("lkj(1)", class = "cor")
)

acc_mod_data <- clean_2 |>
  mutate(
    correct.num = ifelse(correct == TRUE, 1, 0),
    trial.num = trial - 4
  ) |>
  filter(type != "practice")
acc_mod <- brm(correct.num ~ trial.num + (trial.num | gameId) + (1 | target),
  family = bernoulli(link = "logit"),
  data = acc_mod_data,
  file = here(mod_loc, "acc_2.rds"),
  prior = acc_priors,
  control = list(adapt_delta = .95)
)
```

```{r}
acc_mod_2 <- read_rds(here(mod_results, "acc_2.rds")) |> mutate(across(c(`Estimate`, `lower`, `upper`), ~ exp(.)))
```

@@

```{r}
speed_priors <- c(
  set_prior("normal(60,100)", class = "Intercept"),
  set_prior("normal(0,20)", class = "b"),
  set_prior("normal(0,20)", class = "sd"),
  set_prior("lkj(1)", class = "cor")
)

speed_mod_data_2 <- clean_2 |>
  mutate(
    time.sec = time / 1000,
    trial.num = trial - 2
  ) |>
  filter(type != "practice")

speed_mod_2 <- brm(time.sec ~ trial.num + (trial.num | gameId) + (1 | target),
  data = speed_mod_data_2,
  file = here(mod_loc, "speed_2.rds"),
  prior = speed_priors,
  control = list(adapt_delta = .95)
)
```

```{r}
speed_mod_2 <- read_rds(here(mod_results, "speed_2.rds"))
```

@@

```{r, eval=F}
description_priors <- c(
  set_prior("normal(5,10)", class = "Intercept"),
  set_prior("normal(0,5)", class = "b"),
  set_prior("normal(0,5)", class = "sd"),
  set_prior("lkj(1)", class = "cor")
)

description_mod_data_2 <- clean_2 |>
  mutate(
    trial.num = trial - 2
  ) |>
  filter(type != "practice")

description_mod_2 <- brm(words ~ trial.num + (trial.num | gameId) + (1 | target),
  data = description_mod_data_2,
  file = here(mod_loc, "description_2.rds"),
  prior = speed_priors,
  control = list(adapt_delta = .95)
)
```

```{r}
description_mod_2 <- read_rds(here(mod_results, "description_2.rds"))
```

@@

```{r}
conv_priors <- c(
  set_prior("normal(.5,.2)", class = "Intercept"),
  set_prior("normal(0,.1)", class = "b"),
  set_prior("normal(0,.05)", class = "sd")
)

@@

sim_across_between_mod_2 <- brm(sim ~ same_game + same_speaker + (1 | target),
  data = sim_across_between_data_2,
  file = here(mod_loc, "sim_across_between_2.rds"),
  prior = conv_priors,
  control = list(adapt_delta = .95)
)

sim_to_last_data_2 <- sims_2 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == 4) |>
  mutate(
    same_speaker = ifelse(speaker1 == speaker2, 1, 0),
    earlier_block.num = earlier - 1
  )

sim_to_last_mod_2 <- brm(sim ~ earlier_block.num + same_speaker + (1 | game1) + (1 | target),
  data = sim_to_last_data_2,
  file = here(mod_loc, "sim_to_last_2.rds"),
  prior = conv_priors,
  control = list(adapt_delta = .95)
)

sim_to_next_data_2 <- sims_2 |>
  filter(game1 == game2) |>
  mutate(later = ifelse(block1 > block2, block1, block2), earlier = ifelse(block1 > block2, block2, block1)) |>
  filter(later == earlier + 1) |>
  mutate(
    same_speaker = ifelse(speaker1 == speaker2, 1, 0),
    earlier_block.num = earlier - 1
  )

sim_to_next_mod_2 <- brm(sim ~ earlier_block.num + same_speaker + (1 | game1) + (1 | target),
  data = sim_to_next_data_2,
  file = here(mod_loc, "sim_to_next_2.rds"),
  prior = conv_priors,
  control = list(adapt_delta = .95)
)

sim_across_data_2 <- sims_2 |>
  filter(game1 != game2) |>
  filter(block1 == block2) |>
  mutate(block.num = block1 - 1)

sim_across_mod_2 <- brm(sim ~ block.num + (1 | target),
  data = sim_across_data_2,
  file = here(mod_loc, "sim_across_2.rds"),
  prior = conv_priors,
  control = list(adapt_delta = .95)
)
```
